---
title: "Embayment MANOVA"
output: html_notebook
---
This is to perform a MANOVA on the cleaned and log transformed data from the output of the embayment analysis.
The imported dataset should only contain the columns ('Embayment', 'Type 1', 'Lm', 'Lb' , 'C').
The last three of which should be normally distributed (after log transform in this case).
First we will import the data.

```{r}
library('readr')
library('dplyr')
setwd('/Users/tinabaum/Documents/Projects/Python/EmbaymentProcessing/')
df <- readr::read_csv('./DataOutput/LogTidyData.csv')
names(df)[names(df) == 'Type 1'] = 'EmbClass'
summary(df)
```


Next we will plot the qqplots to make sure data is normally distributed.

```{r}
qqnorm(df$Lm)
qqline(df$Lm, col = 'steelblue', lwd=2)
```
```{r}
qqnorm(df$Lb)
qqline(df$Lb, col = 'steelblue', lwd=2)
```

```{r}
qqnorm(df$C)
qqline(df$C, col = 'steelblue', lwd=2)
```

Once we have established that the data is roughly normally distributed we can conduct the MANOVA and post hoc tests.

```{r}
df.maov <- manova(cbind(Lm, Lb) ~ EmbClass, data = df)
summary(df.maov)
```
```{r}
summary.aov(df.maov)
```

Now that we know that they are both significant we can do one-way ANOVAS and post-hoc tests.
```{r}
Lm.lm <- lm(df$Lm ~ df$EmbClass, data = df)
Lm.aov<- aov(Lm.lm)
summary(Lm.aov)
```
```{r}
Lm.hsd<- TukeyHSD(Lm.aov)
Lm.hsd
```

and for Lb:
```{r}
Lb.lm <- lm(df$Lb ~ df$EmbClass, data = df)
Lb.aov <- aov(Lb.lm)
summary.aov(Lb.aov)
```

```{r}
Lb.hsd <- TukeyHSD(Lb.aov)
Lb.hsd
```

And we will finally perform the same analysis using C ratio

```{r}
C.lm <- lm(df$C ~ df$EmbClass)
C.aov<- aov(C.lm)
summary.aov(C.aov)
```
It is significant so:
```{r}
C.hsd<-TukeyHSD(C.aov)
C.hsd
```

Now we can save the HSD Outputs to a specific folder (EmbaymentProcessing/DataOutpu/R_Data):


```{r}
write.csv(Lm.hsd$`df$EmbClass`, '/Users/tinabaum/Documents/Projects/Python/EmbaymentProcessing/DataOutput/R_Data/Lm_HSD.csv')
write.csv(Lb.hsd$`df$EmbClass`, '/Users/tinabaum/Documents/Projects/Python/EmbaymentProcessing/DataOutput/R_Data/Lb_HSD.csv')
write.csv(C.hsd$`df$EmbClass`, '/Users/tinabaum/Documents/Projects/Python/EmbaymentProcessing/DataOutput/R_Data/C_HSD.csv')
```

