---
title: "Embayment MANOVA"
output: html_notebook
---
This is to perform a MANOVA on the cleaned and log transformed data from the output of the embayment analysis.
The imported dataset should only contain the columns ('Embayment', 'Type 1', 'Lm', 'Lb' , 'C').
The last three of which should be normally distributed (after log transform in this case).
First we will import the data.

```{r}
library('readr')
library('dplyr')
setwd('/Users/tinabaum/Documents/Projects/Python/EmbaymentProcessing/')
df <- read_csv('./DataOutput/LogTidyData.csv')
names(df)[names(df) == 'Type 1'] = 'EmbClass'
summary(df)
```

```{r}
tapply(df$C, df$EmbClass, summary)
```


Next we will plot the qqplots to make sure data is normally distributed.

```{r}
qqnorm(df$LmLog)
qqline(df$LmLog, col = 'steelblue', lwd=2)
```
```{r}
qqnorm(df$LbLog)
qqline(df$LbLog, col = 'steelblue', lwd=2)
```

```{r}
qqnorm(df$CLog)
qqline(df$CLog, col = 'steelblue', lwd=2)
```

Once we have established that the data is roughly normally distributed we can conduct the MANOVA and post hoc tests.

```{r}
df.maov <- manova(cbind(LmLog, LbLog) ~ EmbClass, data = df)
summary(df.maov)
```
```{r}
summary.aov(df.maov)
```

Now that we know that they are both significant we can do one-way ANOVAS and post-hoc tests.
```{r}
LmLog.lm <- lm(df$LmLog ~ df$EmbClass, data = df)
LmLog.aov<- aov(LmLog.lm)
summary(LmLog.aov)
```
```{r}
LmLog.hsd<- TukeyHSD(LmLog.aov)
LmLog.hsd
```

and for Lb:
```{r}
LbLog.lm <- lm(df$LbLog ~ df$EmbClass, data = df)
LbLog.aov <- aov(LbLog.lm)
summary.aov(LbLog.aov)
```

```{r}
LbLog.hsd <- TukeyHSD(LbLog.aov)
LbLog.hsd
```

And we will finally perform the same analysis using C ratio

```{r}
CLog.lm <- lm(df$CLog ~ df$EmbClass)
CLog.aov<- aov(CLog.lm)
summary.aov(CLog.aov)
```
It is significant so:
```{r}
CLog.hsd<-TukeyHSD(CLog.aov)
CLog.hsd
```

Now we can save the HSD Outputs to a specific folder (EmbaymentProcessing/DataOutpu/R_Data):


```{r}
write.csv(Lm.hsd$`df$EmbClass`, '/Users/tinabaum/Documents/Projects/Python/EmbaymentProcessing/DataOutput/R_Data/Lm_HSD.csv')
write.csv(Lb.hsd$`df$EmbClass`, '/Users/tinabaum/Documents/Projects/Python/EmbaymentProcessing/DataOutput/R_Data/Lb_HSD.csv')
write.csv(C.hsd$`df$EmbClass`, '/Users/tinabaum/Documents/Projects/Python/EmbaymentProcessing/DataOutput/R_Data/C_HSD.csv')
```

